HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

Source sentences are all in English, and the UCCA annotation was performed by four
computational linguists and one linguist.

For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech. In order to allow us to calculate IAA also for
the Czech annotations we recruited several further annotators to work on a small number of 
sentences each. We treat these further annotators as one annotator, giving us two annotators
for each language pair.
The annotators were all native  speakers of the respective target languages and fluent in English.

In \tabref{tab:annot},
we show the total number of sentences and nodes annotated by each annotator. Note that not all nodes in all sentences were annotated. Sometimes this was because the
annotator did not finish a node, or accidentally missed a node, but in many cases it was also because it was an implicit 
UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
\end{center}
\end{table}

@@

\oa{what is the purpose of the BLEU binning? is it because low quality and high
quality translations often diverge in their agreement scores?}

@@

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to review\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved.}

@@

\XXX{Omri: I would consider adding further examples from the Google Doc. For instnace
``your risk of falling'' -- ``Ihr Risiko''.
Ondrej: I don't see any HMEANT problem here, the whole NP 'your risk of falling'
is aligned with 'Ihr Risiko' and HMEANT allows to indicate that the match was
partial, to that's probably what everyone would choose. I've put the other
example higher, but please have a look, I'm not sure if we should keep it there
at all.}

>>>>

Source sentences are all in English, and their UCCA annotation was performed by four
computational linguists and one linguist.

For the annotation of the MT output, we recruited two annotators for each of German, Romanian
and Polish and one main annotator for Czech.
%In order to allow us to calculate
For IAA also for
the Czech, we recruited several further annotators to work on a small number of 
sentences each. We treat these further annotators as one annotator, giving us two annotators
for each language pair.
The annotators were all native  speakers of the respective target languages and fluent in English.

\tabref{tab:annot}
shows the total number of sentences and nodes annotated by each annotator. Note
that not all nodes in all sentences were annotated. Sometimes,
%this was because
the annotator did not finish a sentence or accidentally missed a node, but in many cases it was also because it was an implicit 
UCCA node, which was not shown to the annotators since there is no corresponding source segment.
\begin{table}
\begin{center}
{\small
\begin{tabular}{ll|cccc}
& & cs & de & pl & ro \\
\hline
Sentences &  Annot. 1 & 324   & 339  & 351  & 230  \\
 & Annot. 2 & 205 & 104  & 340  & 337 \\
\hline
Nodes & Annot. 1 & 8794  & 9253 & 9557  & 6152 \\
 &Annot. 2 & 5553 & 2906  & 9303  & 9228  \\
\end{tabular}
}
\caption{Total numbers of sentences and nodes annotated on the MT output.}
\label{tab:annot}
\end{center}
\end{table}

@@

%\oa{what is the purpose of the BLEU binning? is it because low quality and high
%quality translations often diverge in their agreement scores?}

@@

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to review\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved. So Ondrej would actually
  *remove* this example, because it would illustrate HMEANT's problems only if
  the meaning was correct.}

@@
